# Swirl


### Swirl

**Swirl** is a package for learning R interactively within RStudio.

Instead of reading instructions on a webpage and then switching between your browser and RStudio, Swirl gives you interactive lessons directly in R.

Begin by installing the `swirl` package.

Type the following command into the **Console**:

```{r, eval=FALSE}
install.packages("swirl")
```

Wait for the installation to finish.

Once the installation is complete, load the package:

```{r, eval=FALSE}
library("swirl")
```

Then start Swirl by typing:

```{r, eval=FALSE}
swirl()
```

Swirl will begin interacting with you. Simply read the instructions on the screen and enter your responses.



BELOW IS OLD MASH CONTENT


"Swirl" is a package for learning ***R*** interactively within ***RStudio***.

Begin by installing the <code style="color: blue;">swirl</code> package by typing the following command into the console:

<center>
    <code style="color: blue;">install.packages("swirl")</code>
</center>

Once the installation is complete, launch the <code style="color: blue;">swirl</code> package by typing

<center>
    <code style="color: blue;">library("swirl")</code>
</center>

From here <code style="color: blue;">swirl</code> will automatically begin interacting with you. Simply read the instructions on the screen and enter your responses.
